### 2014-02-19 thesis/src/chapters/chapter-implementation.tex
Thesis: Finish technical overview in the implementation chapter

  \item Auto-scaling subsystem
    \begin{asparaenum}
    \item[\textbf{OpenNebula}]
    \item[\textbf{OpenNebula AppFlow/AppStage ?}]
    \item[\textbf{Chef}]
    \item[\textbf{OpenVZ (drivers)}]
    \end{asparaenum}
\end{itemize}

>>>>

  \item Auto-scaling subsystem
    \begin{asparaenum}
    \item[\textbf{OpenNebula}] There was a need for a tool that would be used for efficient management of the resources of a data center. OpenNebula is an open source respond to this need -- first released in 2008, with good support from the community, seemed a good candidate for a tool. Our familiarity with it was an additional factor which influenced our final choice of OpenNebula as the tool for the job.
    \item[\textbf{Chef}] As manual virtual machines provisioning is a tedious and error-prone task, this is a perfect match for a tool that would automate the process. We chose \emph{Chef} as it is written in the language of the whole platform (i.e. Ruby), mature (initially released in 2009) and widely used tool. \footnote{According to the website of the product (\url{http://www.getchef.com/customers/}), it is used by such companies as Facebook, BlueKai or BookRenter. More can be found at the provided URL.}
    \item[\textbf{OpenVZ (drivers)}] The significance of choosing linux containers as a virtualisation technology was fully described in the preceding chapters. However, the drivers for the OpenVZ are not supported by the OpenNebula maintainers, so we had to use our own-developed tool while taking a course at the university. This tools forms an official add-on for OpenNebula 3.8.
    \end{asparaenum}
\end{itemize}
